Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-07-13 main.tex
:pencil: Update manuscript

\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{pin}{PIN}{Positive Intrinsic-Negative}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{tg}{TG}{tag}
\newacronym{ue}{UE}{user}

@@

\begin{abstract}
	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of ambient signals.
	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	We uniquely introduce \emph{Metascatter} that adapts the input distribution of a finite-state passive backscatter node based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by surrounding radio-frequency waves.
	% Compared to conventional \gls{irs}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
	Compared to existing \gls{irs}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{irs} via smart input design.
	% Compared to \gls{irs}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
	% Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
	It not only reduces hardware complexity and optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
	Moreover, we consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple Metascatters.
	For simplicity, it is assumed the user first jointly decodes all backscatter messages based on average received power, then models reflection patterns and backscatter paths within equivalent channel for primary decoding.
	% Once modulation uncertainty of Metascatters are eliminated, models contributions from additional paths within equivalent channel
	% decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
	% For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
	We characterize achievable primary-(total-)backscatter rate regions by jointly design input distribution at Metascatters, active beamforming at AP, and decision regions at user.
	% A suboptimal \gls{bcd} algorithm was proposed, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is optimized by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
	A suboptimal \gls{bcd} algorithm was proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is optimized by \gls{pgd} with backtracking line search, and convex decision regions are refined by \gls{dp}.
	% the decision regions are restricted as convex then optimized by \gls{dp}.
	% A suboptimal \gls{bcd} algorithm was proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is optimized by \gls{pgd} with backtracking line search, and the decision thresholds are optimized by \gls{dp}.
	Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via input design.
\end{abstract}

\begin{section}{Introduction}
	\IEEEPARstart{B}{ackscatter} is recently re-innovated as a promising approach to support low-power communications and control wireless propagation environments.
	% The concept of \gls{ambc} was first proposed in \cite{Liu2013b}, where battery-free communication between passive nodes was established by
	\gls{ambc} that enables battery-free communication between passive nodes was first proposed in \cite{Liu2013b}, where battery-free communication between passive nodes was established by

	Battery-free communication between passive nodes was first by

	each tag harvests energy from and modulates information over ambient \gls{rf} signals by periodically switching between different reflection patterns.
	It enables battery-free communication between fully passive nodes, but the backscatter signal strength can be relatively weak and the decoding is subject to strong direct-link interference.
	To solve this, \cite{Yang2018d} exploited the repeating structure of \gls{ofdm} symbol for interference cancellation based on backscatter channel strength.
	Cooperative primary-backscatter decoding using co-located receiver, known as cooperative \gls{ambc}, was proposed in \cite{Yang2018}.
	The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channels, and proposed a low-complexity \gls{ml} detector for frequency-selective fading channels with ambient \gls{ofdm} carrier.
	When transmit cooperation is also available, cooperative \gls{ambc} is more commonly known as \gls{sr} \cite{Liang2020}.
	The authors of \cite{Guo2019b} classified \gls{sr} into commensal, parasitic, and competitive modes based on the relative link priority, then derived their instantaneous achievable rate and optimal power allocation.
	The outage probability for those modes was later studied in \cite{Ding2020}.
	On the other hand, it was concluded in \cite{Long2020a} that if the backscatter symbol period is much longer than the primary symbol period, then the non-coherent achievable rate of primary decoding would approach that of the coherent case.
	The authors also considered the transmit precoder design for weighted total-rate maximization and transmit power minimization problems.
	\cite{Zhou2019a} explored how the number of transmit antennas, receive antennas, and symbol period ratio asymptotically influence the ergodic rate of primary and backscatter links.
	With multi-antenna at all ends, \cite{Wu2021a} optimized the transmit precoder to maximize the backscatter achievable rate under primary rate constraint.
	However, those paper only considered single tag scenario and the optimal tag multiple access scheme remains unknown.
	\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and studied the receive combiner design when the receiver decodes in the order of equivalent channel strength.
	A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, and energy efficiency maximization was considered with respect to transmit power, reflection efficiency, and time allocation design.
	In \cite{Han2021}, random code-assisted backscatter multiple access was combined with \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.

	On the other hand, \gls{irs} has recently emerged as a promising technique to enhance the energy efficiency.
	In practice, an \gls{irs} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
	Different from relay, backscatter and frequency-selective surface \cite{Anwar2018}, \gls{irs} assists the primary transmission using passive components with much lower energy consumption and thermal noise, but is limited to frequency-dependent reflection.
	\cite{Wu2018} proposed an \gls{irs}-assisted \gls{miso} system and jointly optimized the precoder and the phase shifts to minimize the transmit power.
	The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
	In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice.
	To estimate the cascaded link without \gls{rf}-chains at the \gls{irs}, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
	\gls{irs} was also added to single-tag and multi-tag \gls{sr} systems to improve backscatter efficiency \cite{Chen2021,Zhang2021d}.
	Recently, the idea of \gls{irs}-empowered \gls{sr} was proposed in \cite{Xu2020b,Hua2022}, where the reflection pattern can be decoupled as the multiplication of whole phase shift matrix and one backscatter symbol.
	The idea was combined with spatial modulation to divide the \gls{irs} into reflection and information and elements, and the error performance of non-coherent backscatter detection was studied accordingly \cite{Hu2021a}.

>>>>

\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{pin}{PIN}{Positive Intrinsic-Negative}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{tg}{TG}{tag}
\newacronym{ue}{UE}{user}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}

@@

\begin{abstract}
	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of ambient signals.
	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	We uniquely introduce \emph{Metascatter} that adapts the input distribution of a finite-state passive backscatter node based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by surrounding waves.
	% Compared to conventional \gls{irs}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
	Compared to existing \gls{irs}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{irs} via smart input design.
	% Compared to \gls{irs}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
	% Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
	This not only reduces hardware complexity and optimization cost, but also enables a flexible tradeoff between primary (legacy) and backscatter links using shared spectrum, energy, and infrastructures.
	Moreover, we consider a specific scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple Metascatters.
	For simplicity, it is assumed the user first jointly decodes all backscatter messages based on average received power, then models reflection patterns and backscatter paths within equivalent channel for primary decoding.
	% Once modulation uncertainty of Metascatters are eliminated, models contributions from additional paths within equivalent channel
	% decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
	% For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at Metascatters, the active beamforming at the AP, and the decision regions at the user.
	% A suboptimal \gls{bcd} algorithm was proposed, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is optimized by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
	A suboptimal \gls{bcd} algorithm is proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is updated by \gls{pgd}, and the suboptimal convex decision regions are refined by \gls{dp}.
	% A suboptimal \gls{bcd} algorithm was proposed with the \gls{kkt} input distribution evaluated in closed form, the active beamforming updated by \gls{pgd}, and the decision regions restricted to convex then refined by \gls{dp}.
	% the decision regions are restricted as convex then optimized by \gls{dp}.
	% A suboptimal \gls{bcd} algorithm was proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is optimized by \gls{pgd} with backtracking line search, and the decision thresholds are optimized by \gls{dp}.
	Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via input design.
\end{abstract}

\begin{section}{Introduction}
	\IEEEPARstart{B}{ackscatter} is recently re-innovated as a promising approach to support low-power communications and control wireless propagation environments.
	% \IEEEPARstart{B}{ackscatter} is re-innovated to support low-power communications and control wireless propagation environments.
	% \IEEEPARstart{B}{ackscatter} allows wireless nodes to recycle existing .
	% \IEEEPARstart{B}{ackscatter} allows wireless nodes to communicate without generating carrier.
	% The concept of \gls{ambc} was first proposed in \cite{Liu2013b}, where battery-free communication between passive nodes was established by
	\gls{ambc} that enables battery-free communication between interactive nodes was first introduced and prototyped in \cite{Liu2013b}, where devices harvest energy from and modulate information over ambient \gls{rf} signals by switching between reflecting and absorbing states.
	To combat the strong direct-link interference of \gls{ambc}, \cite{Yang2018d} exploited the repeating structure of \gls{ofdm} symbol and proposed a multi-antenna detector that only requires the backscatter channel strength.
	% with periodical change of states.
	% each tag harvests energy from and modulates information over ambient \gls{rf} signals by periodically switching between different reflection patterns.
	% It enables battery-free communication between fully passive nodes, but the backscatter signal strength can be relatively weak and the decoding is subject to strong direct-link interference.
	% To solve this, \cite{Yang2018d} exploited the repeating structure of \gls{ofdm} symbol for interference cancellation based on backscatter channel strength.
	% Using co-located receiver to decode
	Cooperative \gls{ambc} that decodes primary and backscatter links using co-located receiver was proposed in \cite{Yang2018}, where the authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channels and proposed a low-complexity \gls{ml} detector for frequency-selective fading channels.
	The concept was then generalized to \gls{sr} in \cite{Liang2020} to ``exploit the benefits and address the drawbacks'' of \gls{cr} and \gls{ambc}.
	% The concept of \gls{sr} was then proposed in \cite{Liang2020} to exploit
	% symbiotic radio (SR), is proposed to ex- ploit the benefits and address the drawbacks of cognitive radio (CR) and ambient backscattering communications (AmBC)
	% When transmit cooperation is also available, cooperative \gls{ambc} is also termed as \gls{sr} \cite{Liang2020}.
	The authors of \cite{Guo2019b} classified \gls{sr} into commensal, parasitic, and competitive types based on link priority, and derived their instantaneous rates and optimal power allocations.
	The corresponding outage probabilities were also studied in \cite{Ding2020}.
	Besides, \cite{Long2020a} concluded that if the backscatter symbol period is sufficiently long, then the non-coherent primary rate would approach its coherent counterpart.
	The authors thus proposed to decode the primary link under backscatter uncertainty, then perform \gls{sic} and decode the backscatter link.
	% The authors also considered the transmit precoder design for weighted total-rate maximization and transmit power minimization problems.
	% \cite{Zhou2019a} explored how the number of transmit antennas, receive antennas, and symbol period ratio asymptotically influence the ergodic rate of primary and backscatter links.
	\cite{Zhou2019a} explored the impact of transmit antennas, receive antennas, and backscatter symbol period on the ergodic rate of primary and backscatter links.
	For multi-antenna at all ends, \cite{Wu2021a} optimized transmit beamforming to maximize the backscatter achievable rate under primary rate constraint.
	However, those paper only considered single backscatter node and backscatter multiple access remains an open issue.
	In \cite{Xu2021a}, a \gls{noma}-based \gls{sr} was proposed and receive combining was investigated for \gls{sic} order in equivalent channel strength.
	% \cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and investigated receive beamforming when \gls{sic} order is determined by equivalent channel strength.
	% \cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and studied the receive combiner design when the receiver decodes in the order of equivalent channel strength.
	% A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, and energy efficiency maximization was considered with respect to transmit power, reflection efficiency, and time allocation design.
	A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, where transmit power, reflection efficiency, and time allocation was optimized to maximize energy efficiency.
	% In \cite{Han2021}, random code-assisted backscatter multiple access was combined with \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.
	To reduce coordination between passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.

	% On the other hand, \gls{irs} has recently emerged as a promising technique to enhance the energy efficiency.
	% In practice, an \gls{irs} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
	% Different from relay, backscatter and frequency-selective surface \cite{Anwar2018}, \gls{irs} assists the primary transmission using passive components with much lower energy consumption and thermal noise, but is limited to frequency-dependent reflection.
	% On the other hand, \gls{irs} consists of numerous sub-wavelength passive elements that alter propagation environment using adaptive backscatter pattern to assist existing networks. Extensive research has been devoted to optimizing the reflection coefficient
	On the other hand, \gls{irs} consists of numerous sub-wavelength passive elements with adaptive amplitudes and/or phases that alter propagation environment to assist existing networks.
	Extensive research has been devoted to optimizing the phases of \gls{irs} during whole channel block for different metrices, as TODO \cite{Wu2018,Wu2019a,Wu2019}.
	% In contrast, dynamic passive beamforming that adjusts \gls{irs} within channel block was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
	% In contrast, dynamic passive beamforming that adjusts \gls{irs} over finer time slots was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
	Besides, dynamic passive beamforming that adjusts \gls{irs} over fine-grained slots within channel coherence time was proposed for \gls{ofdm} systems in \cite{Yang2020}.

	The idea was further applied to \gls{wpcn} to strike the

	proactively generate favourable time-varying channels by properly designing the IRS phase-shift vectors over different time slots,
	which thus enhances the multiuser diversity over time and also allows more flexible resource allocation.

	mic IRS beamforming is actually beneficial for maximizing the throughput
	of WPCNs
	% The authors
	% of [29] considered a novel dynamic passive beamforming for
	% Orthogonal Frequency-Division Multiplexing (OFDM) systems,
	% where the reflection coefficient is varied over consequent
	% time slots to enable flexible resource allocation over timefrequency Resource Blocks (RBs).

	further adjusted the IRS reflection pattern within channel coherence time to mimic multi-beam reflection in a time-division manner

	\cite{Wu2018} proposed an \gls{irs}-assisted \gls{miso} system and jointly optimized the precoder and the phase shifts to minimize the transmit power.
	The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
	In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice.
	To estimate the cascaded link without \gls{rf}-chains at the \gls{irs}, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
	\gls{irs} was also added to single-tag and multi-tag \gls{sr} systems to improve backscatter efficiency \cite{Chen2021,Zhang2021d}.
	Recently, the idea of \gls{irs}-empowered \gls{sr} was proposed in \cite{Xu2020b,Hua2022}, where the reflection pattern can be decoupled as the multiplication of whole phase shift matrix and one backscatter symbol.
	The idea was combined with spatial modulation to divide the \gls{irs} into reflection and information and elements, and the error performance of non-coherent backscatter detection was studied accordingly \cite{Hu2021a}.
